The \dealii{} Library, Version 9.0

### 2018-04-07 9.0/paper.tex
Fix two typos.

\item
  C++11 is now required and used in many places. For performance reason,
  move semantics is used when possible and in many places, \texttt{emplace\_back} 
  replaces \texttt{push\_back()}. C-style raw pointers have been replaced by
  \texttt{shared\_ptr} and \texttt{unique\_ptr} to avoid the risk of memory leak.
  Private constructors have been removed and instead were delete. clang-tidy is
  now being used to ensure the quality of the code.

\item
  Improved support for LinearOperator (Trilinos payload, Schur complement,
  iterative inverse), removal of old wrapper classes

>>>>

\item
  \dealii{} first offered support for C++11 features in version 6.2, which was
  published in 2009: This release is the first to \emph{require} a compiler
  supporting C++11. \dealii{} now uses language improvements such as using
  \texttt{emplace\_back()} instead of \texttt{push\_back()}, moving objects
  instead of copying them, using \texttt{nullptr} instead of \texttt{NULL}, and
  marking unimplemented constructors with \texttt{=delete;} instead of making
  them \texttt{private}. These changes include some minor incompatibilities: all
  \texttt{clone} functions (such as \texttt{FiniteElement::clone} and
  \texttt{Mapping::clone}) now return \texttt{std::unique\_ptr}s instead of
  C-style raw pointers. Indeed, nearly every interface that returns a pointer
  now returns either a \texttt{std::shared\_ptr} or \texttt{std::unique\_ptr},
  which clarifies object ownership responsibilities and avoids memory leaks.

\item \dealii{} has made extensive use of both the clang-tidy and coverity
      static analysis tools for detecting bugs and other issues in the code.
      %% TODO is there somewhere we can cite for either of these tools? It would
      %% be nice to recognize the department of homeland security for offering
      %% coverity.
      %% TODO at the time of writing this coverity is down; get an issue count
      %% when it is back online.

\item
  \texttt{LinearOperator}, a flexible template class that implements the action of a
  linear operator (see \cite{MaierBardelloniHeltai-2016-b}), now supports
  computations with Trilinos, Schur complements, and linear constraints. This
  class is, as of this release, the official replacement for about half a dozen
  similar (but less general) classes, such as \texttt{FilteredMatrix},
  \texttt{IterativeInverse}, and \texttt{PointerMatrix}.
